A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}

### 2019-02-13 reviewer_response.tex

\documentclass[]{article}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage[version=4]{mhchem}
%opening
\title{\normalsize \textbf{Response to the Reviewer’s Comments on Manuscript FPE-D-18-00720}}
\author{}
\date{}

\begin{document}
\doublespacing
\maketitle

To: Prof. Jeffrey Potoff

Associate Editor

Fluid Phase Equlibria
\vspace{0.3cm}

Dear Prof. Jeffrey Potoff:

\hspace{0.5cm}Thank you for your message forwarding the reviewers’ comments on our manuscript entitled \textit{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}. We have carefully addressed the comments and suggestions of the reviewers, which required us to make changes in the text. The most substantial revision took place in section 5.3, for which we carried out additional simulations. In addition, we included the names of the ionic liquids and changed the acronym of one of the anions. To facilitate
your evaluation, we have crossed out all removed text and incorporated new content in color blue.

\hspace{0.5cm}Please find attached our detailed answers to the comments of each reviewer. We
hope that the revised version of the manuscript is suitable for publication.

\hspace{0.5cm}Sincerely yours,
\vspace{0.5cm}

Prof. Charlles R. A. Abreu

Federal University of Rio de Janeiro

\section{\textbf{Reviewer \#1}}
{\color{blue}{The manuscript submitted by Silveira \textit{et al.} presents their computational work on the study of solubility primarily of \ce{CO_2} but also for some additional compounds in ILs. They focus on the simulation of \ce{[emim][B(CN)_4]} IL in a comparative manner to \ce{[emim][NTF_2]} IL, using various existing force fields for the former and implementing simplifications in the simulation of the systems under study by introducing rigid body representations for the ions and by using the damped shifted force method to handle the electrostatics. The manuscript is suitable to be published in your journal, after addressing some problems: }}

\textbf{Answer}: We thank the reviewer for careful reading our manuscript and for the valuable comments and suggestions. We have tried to address them in the best possible way, considering the proposed scope of our work. Please find attached an annotated version of the revised manuscript. This is the one whose pages are mentioned in the answers that follow bellow.

{\color{blue}{1) The authors chose not to use an iterative scheme to correct the pressure of their simulations. They should justify their choice by including quantitative information from their simulations on how this correction would affect both the differences in the free energy but also the system's density at high concentrations.}}

\textbf{Answer}: Instead of performing an iterative scheme, we were able to correct the equilibrium pressure by using the technique of reweighting, as explained in page 4 of the manuscript. Although the correction term resulted to be small, this suggestion has allowed us to present the results in a rigorous way with considerable less computational effort, in comparison to the iterative scheme.

{\color{blue}{2) Among the various existing models used in this work, some explicitly report the use of LJ long range corrections in the energy and pressure. The authors should clearly state if they have taken that into account in their simulations.}}

\textbf{Answer}: The reviewer is right. We applied analytic tail corrections to the LJ interactions for all systems investigated. This information has been included in page 5 of the manuscript.

{\color{blue}{3) Results on densities of the various IL models at 298 K (Table 1) differ from the ones reported in the initial references. For example,  an 1\% error is presented in this manuscript for the FF-3 model of Koller \textit{et al.}, while an excellent agreement with the experimental density is reported in the original paper of Koller and his co-workers. The authors should explain this discrepancy.}}

\textbf{Answer}: The differences in density between our results and those reported by Koller \textit{et al.} \cite{Koller_2012}, Batista \textit{et al.} \cite{Batista_2015}, Liu \textit{et al.} \cite{Liu_2014} and Weber and Kirchner \cite{Weber_2016} are, respectively: 1 \% , 6.2 \%, 1.8 \% and 0.5 \%.
With the exception of the force field due to Batista \textit{et al.} \cite{Batista_2015}, the discrepancies are not considerable.
In general, we carefully followed the simulation setup reported by those authors, except for the number of ion pairs and the software package. For instance, Koller and co-workers \cite{Koller_2012} simulated 58 ions pairs using GROMACS, while we considered 250 ion pairs and the LAMMPS software package.
Small differences are then expected.
The discrepancy with the results of Batista and co-workers \cite{Batista_2015} stands out  from the others. In this case, however, important computational details are missing in the original paper, such as the method for computing electrostatic interactions, as well as the factors for scaling the 1-4 non-bonded interactions. 
Considering these various factors, we did not focus on reproducing the results of these references, but rather to use the force field parameters reported by the corresponding authors in order to find those that best reproduce the experimental Henry constant of \ce{CO_2}.

{\color{blue}{4) Simulating hybrid systems that include both rigid and non rigid bodies is complex and tricky. The authors should describe in detail how they performed these simulations in terms of barostatting and thermostatting.}}

\textbf{Answer}: In page 5 of the manuscript we specify the numerical integrators used to carry out the MD simulations. Considering hybrid systems of flexible and rigid molecules is straightforward in LAMMPS, since it allows to define groups of molecules and apply a different numerical integrator to each group.

{\color{blue}{5)It would be interesting if at least for the case of CO2 an isotherm was calculated and included in the paper.}}

\textbf{Answer}: We agree with the reviewer that computing an isotherm would be interesting. However, this computation requires to carry out extra simulations for different numbers of solute molecules, which is beyond the scope of this work.

\section{\textbf{Reviewer \#2}}

{\color{blue}{In the present manuscript, Silveira \textit{et al.} performed a systematic comparison of force fields used in Molecular Dynamic (MD) simulations of the solvation of carbon dioxide (\ce{CO_2}) and other compounds in two ionic liquids (ILs). For this purpose, solvation energies, Henry constants, and activity coefficients were calculated based on solid methodologies. A detailed review of the literature with respect to the theoretical background and the force fields is provided. Simplifications in the simulation strategies are analyzed by treating the IL ions as rigid instead of flexible bodies. A structural analysis of the molecular systems and their relationships with the studied properties are investigated thoroughly from a physico-chemical point of view. The authors could demonstrate that the IL \ce{[emim][B(CN)_4]} shows the largest solubility for \ce{CO_2} in comparison to other common ILs. Overall, the scientific findings are very clear, concise, and of high quality, and are presented in a good English. Formalities according to the guidelines of the journal are also fulfilled. In conclusion, the present manuscript is definitely worthy of publication taking into consideration a few minor comments from my side.}}

We are grateful for the comments and suggestions of the second reviewer.

{\color{blue}{1. In the context of the simulation protocol, information on the number simulation runs and the use of the mixing rules for the Lennard-Jones interactions should be given. The authors should also specify how the uncertainties of the various properties were calculated.}}

\textbf{Answer}: Instead of the number of runs, in page 6 we included the total simulation time for each system, since it might be a more informative measure of computational effort. The information about mixing rules and uncertainties calculations have been included in pages 5, 9 and 12.

{\color{blue}{2. The authors were focusing on several static properties for the pure ILs using different models. As reference property for force field validation, the density was selected where deviations between about (1 and 5) \% were found according to Table 1. Did the authors also study dynamic properties such as the self-diffusion coefficient and compare the results with the experiment? If so, a corresponding brief paragraph should be included in the revised manuscript. Relative deviations of 5\% in the liquid density can often come along with deviations of several dozens of percent for dynamic properties.
}}

\textbf{Answer}:We haven't done a study of dynamic properties. We have mainly focused on predicting solvation properties given the potential of the investigated ionic liquids in separation processes for \ce{CO_2}.

{\color{blue}{3. The results for the simulated solvation free energies of benzene, hexane, and water showed relatively large deviations from experimental data in the order of 10 \%, while the results for ethanol match. However, for the infinite-dilution activity coefficient of these solutes in the IL [emim][B(CN)4], hexane deviates significantly stronger than benzene, ethanol, and water. It would be interesting to discuss in some more detail why these different trends can be found by considering, for example, the force fields of the pure solute and the mixing rules for the binary mixtures. For sure, it seems that the authors will continue such investigations in their future studies.}}

\textbf{Answer}: The reviewer is right and in order to analyze the strong deviation observed for hexane, we computed an experimental solvation free energy of this solute in  \ce{[emim][B(CN)_4]}, as shown in page 14. The results from simulation show a favorable solvation, in contradiction with the experimental data. That is why we emphasize in the conclusions that a future revision of the models used for the solutes is necessary.

{\color{blue}{4. For the specification of the pressure, the symbol “p” instead of “P” should be used. Furthermore, the unit of the pressure should be given in “MPa” instead of “atm."}}

\textbf{Answer}: This has been acknowledged throughout the manuscript.

\bibliographystyle{ieeetr}
\bibliography{reviewer_response.bib}
\end{document}

### 2019-02-13 ionic_liquids.tex
First round of revision

For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} in the liquid phase are obtained at pressure values for which, in principle, the ideal gas assumption might no longer be valid.
In this case, we can compute the chemical potential of the solute in the real gas phase as
\begin{equation}
\label{eq:mu_gas_real}
\mu^{g}_s = \mu^{ig}_s + R T \ln \left(\frac{f^{g}_s}{p_s}\right),
\end{equation}
where $f^{g}_s$ is the fugacity of the solute in the gas phase.
Then, by considering a system at phase equilibrium ($\mu^{l}_s$ = $\mu^{g}_s$), it follows that
\begin{equation}
\label{eq:fgas_d}
f^{g}_s = c_s R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right). 
\end{equation}

Two additional assumptions are made here. First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems investigated) or can be approximated by an ideal solution. Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase. In this case, Eq.~\eqref{eq:fgas_d} becomes
\begin{equation}
\label{eq:equilibrium pressure}
y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s(p) R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right),
\end{equation}
where $y_s$ is the molar fraction of solute in the gas phase ($y_s \rightarrow 1$ for the systems we analyze here) and $B_s$ is the second virial coefficient of the solute.
In the case of \ce{CO_2}, we employ the correlation for $B_s$ developed by Holste \textit{et al}. \cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0 = 23.02991~\mathrm{\frac{cm^3}{mol}}$, $B_1 = -2455.297~\mathrm{\frac{K \cdot cm^3}{mol}}$, and $B_2 = -1.22675 \times 10^7~\mathrm{\frac{K^2 \cdot cm^3}{mol}}$.

The equilibrium pressure will be given by the value for which the function $\Delta G_{\text{sim}}(p) $, defined by Eq.~\eqref{eq:equilibrium pressure}, intersects $\Delta G_{\text{sim}} (p)$, as obtained in simulations. Note that besides  $\Delta G_{\text{sim}}$, we are also considering  variations of $c_s$ with pressure. These computations are greatly facilitated by the technique of reweighting \cite{McDonald1967,McDonald1969}, which uses simulation results from different states to improve the statistics and, particularly important to our case, allows to interpolate expectation values of thermodynamic observables along unsampled states. This implies a significant reduction in computational cost. In particular, we use the Multistate Bennett Acceptance Ratio (MBAR) estimator \cite{Shirts_2008}, which has been successfully used for the purpose of reweighing ~\cite{Aimoli2014, Nichele2018, Schieber2018}.

@@

Using the software TRAVIS \cite{Brehm_2011}, we obtained combined distribution functions (CDFs) of the dihedral angles formed in \ce{[emim]^+} by atoms C1-N2-C5-C6 and atoms C2-N2-C5-C6.
These angles will be referred to as $\psi_1$ and $\psi_2$, respectively.
In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
All CDFs shown in this section were generated from NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using our standard setup (i.e. flexible ions with PPPM Ewald electrostatics).
Initial inspection reveals that, in all cases, $\psi_1$ and $\psi_2$ populate regions of the diagrams around the two straight lines given by
\begin{equation}
\label{eq:dihedral angles}
\psi_2 = \begin{cases}
\psi_1 + 180^\circ & \text{if} \quad \psi_1 \leq 180^\circ \\
\psi_1 - 180^\circ & \text{if} \quad \psi_1 > 180^\circ
\end{cases},
\end{equation}
both corresponding to a coplanar structure formed by atoms C1, C2, N2, and C5.
%There are two such lines in each diagram because atom C6 can be located on either side of the plane.
One can note in Fig.~\ref{fig:dihedrals_emim} that the CDF peaks, which indicate the most likely dihedral angle combinations, lie either precisely above these lines or very close to them.
The largest distortions from coplanarity occur for the Batista \textit{et al}. \cite{Batista_2015} model, as observed by the peak locations in Fig.~\ref{fig:dihedrals_emim}(b).
Despite this, all rigid bodies considered here for \ce{[emim]^+} are built in such a way that atoms C[1-5], H[1-3], and N[1-2] all lie in a single plane.
Therefore, for specifying the torsion of bond N2-C5 it is enough to set a value for $\psi_1$ and then compute $\psi_2$ by means of Eq.~\eqref{eq:dihedral angles}.
All other structural features (bond lengths, bending angles, and hydrogen-involving dihedrals) are taken from the minimum-energy structure obtained for each force field.

@@

Once the rigid body structures have been determined, we carried out NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using the simplified setup (i.e. rigid ions with DSF electrostatics) and all force fields in question.
In Table~\ref{table:props_dsf}, we compare results for density obtained by using the two methodologies.
In all cases, the simplified method displays excellent agreement with the standard one.
In addition, we note that the models of Koller \textit{et al}. \cite{Koller_2012} and Weber and Kirchner \cite{Weber_2016} are the ones that most closely reproduce the experimental density.
In order to perform a more detailed analysis, we have also computed several radial distribution functions (RDFs), some of which are made available as Supplementary Material.
Excellent agreement is also observed in the RDFs obtained with both methods in the case of the models by Koller \textit{et al}. \cite{Koller_2012} and by Batista \textit{et al}. \cite{Batista_2015}.
Small deviations are observed in the case of the Liu \textit{et al}. \cite{Liu_2014} model, but the reproducibility of RDFs by the simplified method is still very good.
%Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
The model of Weber and Kirchner \cite{Weber_2016}, on the other hand, presents RDFs for the pairs C5\textsubscript{cation}-N\textsubscript{anion} (that is, C5\textsubscript{cation} with any nitrogen atom in the anion) and C2\textsubscript{cation}-B\textsubscript{anion} with important discrepancies when rigid bodies are used.
Note that both RDFs are supposed to be affected by the orientations of the ethyl group in the cation.

\begin{table*}
	\centering
	\caption{Comparison of predicted and experimental densities for different models of \ce{[emim][B(CN)_4]} via NpT-MD simulations at $T = 298.0~\text{K}$ and $p = 1.0~\text{atm}$. The experimental density is $1.036~\mathrm{g/cm^3}$ \cite{Doma_ska_2011}.}
	\begin{tabular}{ccccc}
		\hline
		\hline
		\ce{[emim][B(CN)_4]} model                        & 
		\multicolumn{2}{c}{Flexible ions \& PPPM-Ewald} &
		\multicolumn{2}{c}{Rigid ions \& DSF}      \\
		&
		$\rho_\text{sim}$ (g/cm\textsuperscript{3}) &
		error (\%)                                  &
		$\rho_\text{sim}$ (g/cm\textsuperscript{3}) &
		error (\%)                                  \\
		\hline
		Koller \textit{et al}. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
		Batista \textit{et al}. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
		Liu \textit{et al}. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
		Weber and Kirchner \cite{Weber_2016}         & 1.015 & 2.1 & 1.022 & 1.4  \\
		\hline
		\hline
		\label{table:props_dsf}
	\end{tabular}
\end{table*}

@@

A study of conformations was also carried out for \ce{[emim][Tf_2N]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
A CDF obtained for the dihedral angles of sequences C1-N2-C5-C6 and C2-N2-C5-C6 in \ce{[emim]^+}, which is made available in the Supplementary Material, resembles the one in Fig.~\ref{fig:dihedrals_emim}(d).
The resemblance was expected because the intramolecular parameters employed for \ce{[emim]^+} are identical in these two cases, since the corresponding models are both based on the force field developed by Canongia-Lopes and P\'{a}dua \cite{Canongia_Lopes_2006}.
However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][Tf_2N]}.
This highlights the fact that altering atomic charges can induce conformational changes and should, therefore, be accompanied by a revision of torsion parameters in some cases.
With regard to the anion \ce{[Tf_2N]^-}, Deetlefs \textit{et al}. \cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[Tf_2N]^-} is mostly found in its \textit{trans} conformation.
In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[Tf_2N]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}. \cite{Deetlefs_2006}.
This CDF also makes clear that \ce{[Tf_2N]^-} exhibits a considerable degree of flexibility.
Due to this observed behaviors of both ions, all simulations of \ce{[emim][Tf_2N]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$.
The relative error of this result with respect to the experimental value obtained by Tokuda \textit{et al}. \cite{Tokuda_2005} is only 1.12\%.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{Ludwig_anion}
\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[Tf_2N]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][Tf_2N]} at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.}
\label{fig:die_ntf2}
\end{figure}

@@

In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][Tf_2N]} under periodic boundary conditions.
The simulations were carried out at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$.
Table~\ref{table:henry} contains simulated molar densities, partial and total solvation free energies, as well as Henry's law constants ($K_s$) computed via Eq.~\eqref{eq:henry_eq}. The computed values should be compared to the experimental data reported by Mahurin \textit{et al}. \cite{Mahurin_2010} ($K_s = 38.9 \pm 0.03 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}. \cite{Finotello_2008} ($K_s = 39.0 \pm 0.1 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][Tf_2N]}).
The uncertainties in $K_s$ were calculated by using a standard error propagation formula

\begin{equation}
\delta K_s = \beta K_s \sqrt{\left[ \delta^2 (\Delta G_{\text{vdW}}) + \delta^2(\Delta G_{\text{Coul}}) \right]},
\end{equation}
which are a function of the uncertainties in free energy, which are calculate using MBAR \cite{Shirts_2008}.

>>>>

For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} in the liquid phase are obtained at pressure values for which, in principle, the ideal gas assumption might no longer be valid.
In this case, we can compute the chemical potential of the solute in the real gas phase as
\begin{equation}
\label{eq:mu_gas_real}
\mu^{g}_s = \mu^{ig}_s + R T \ln \left(\frac{f^{g}_s}{p_s}\right),
\end{equation}
where $f^{g}_s$ is the fugacity of the solute in the gas phase.
Then, by considering a system at phase equilibrium ($\mu^{l}_s$ = $\mu^{g}_s$), it follows that
\begin{equation}
\label{eq:fgas_d}
f^{g}_s = c_s R T \exp \left( \frac{\Delta G_\text{solv}}{R T} \right). 
\end{equation}

Two additional assumptions are made here. First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems investigated) or can be approximated by an ideal solution. Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase. In this case, Eq.~\eqref{eq:fgas_d} becomes
\begin{equation}
\label{eq:equilibrium pressure}
y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s(p) R T \exp \left( \frac{\Delta G_\text{solv}}{R T} \right),
\end{equation}
where $y_s$ is the molar fraction of solute in the gas phase ($y_s \rightarrow 1$ for the systems we analyze here) and $B_s$ is the second virial coefficient of the solute.
In the case of \ce{CO_2}, we employ the correlation for $B_s$ developed by Holste \textit{et al}. \cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0 = 23.02991~\mathrm{\frac{cm^3}{mol}}$, $B_1 = -2455.297~\mathrm{\frac{K \cdot cm^3}{mol}}$, and $B_2 = -1.22675 \times 10^7~\mathrm{\frac{K^2 \cdot cm^3}{mol}}$.

The equilibrium pressure will be the intersection point between the function $\Delta G_{\text{solv}}(p) $, defined by Eq.~\eqref{eq:equilibrium pressure}, and $\Delta G_{\text{sim}} (p)$, as obtained in simulations. Note that besides  $\Delta G_{\text{sim}}$, we are taking into account variations of $c_s$ with pressure. These computations are greatly facilitated by the technique of reweighting \cite{McDonald1967,McDonald1969}, which uses simulation results from different states to improve the statistics and, particularly important to our case, allows to interpolate expectation values of thermodynamic observables along unsampled states. This implies a significant reduction in computational cost. In particular, we use the Multistate Bennett Acceptance Ratio (MBAR) estimator \cite{Shirts_2008}, which has been successfully used for the purpose of reweighing ~\cite{Aimoli2014, Nichele2018, Schieber2018}.

@@

Using the software TRAVIS \cite{Brehm_2011}, we obtained combined distribution functions (CDFs) of the dihedral angles formed in \ce{[emim]^+} by atoms C1-N2-C5-C6 and atoms C2-N2-C5-C6.
These angles will be referred to as $\psi_1$ and $\psi_2$, respectively.
In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
All CDFs shown in this section were generated from NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using our standard setup (i.e. flexible ions with PPPM Ewald electrostatics).
Initial inspection reveals that, in all cases, $\psi_1$ and $\psi_2$ populate regions of the diagrams around the two straight lines given by
\begin{equation}
\label{eq:dihedral angles}
\psi_2 = \begin{cases}
\psi_1 + 180^\circ & \text{if} \quad \psi_1 \leq 180^\circ \\
\psi_1 - 180^\circ & \text{if} \quad \psi_1 > 180^\circ
\end{cases},
\end{equation}
both corresponding to a coplanar structure formed by atoms C1, C2, N2, and C5.
%There are two such lines in each diagram because atom C6 can be located on either side of the plane.
One can note in Fig.~\ref{fig:dihedrals_emim} that the CDF peaks, which indicate the most likely dihedral angle combinations, lie either precisely above these lines or very close to them.
The largest distortions from coplanarity occur for the Batista \textit{et al}. \cite{Batista_2015} model, as observed by the peak locations in Fig.~\ref{fig:dihedrals_emim}(b).
Despite this, all rigid bodies considered here for \ce{[emim]^+} are built in such a way that atoms C[1-5], H[1-3], and N[1-2] all lie in a single plane.
Therefore, for specifying the torsion of bond N2-C5 it is enough to set a value for $\psi_1$ and then compute $\psi_2$ by means of Eq.~\eqref{eq:dihedral angles}.
All other structural features (bond lengths, bending angles, and hydrogen-involving dihedrals) are taken from the minimum-energy structure obtained for each force field.

@@

Once the rigid body structures have been determined, we carried out NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using the simplified setup (i.e. rigid ions with DSF electrostatics) and all force fields in question.
In Table~\ref{table:props_dsf}, we compare results for density obtained by using the two methodologies.
In all cases, the simplified method displays excellent agreement with the standard one.
In addition, we note that the models of Koller \textit{et al}. \cite{Koller_2012} and Weber and Kirchner \cite{Weber_2016} are the ones that most closely reproduce the experimental density.
In order to perform a more detailed analysis, we have also computed several radial distribution functions (RDFs), some of which are made available as Supplementary Material.
Excellent agreement is also observed in the RDFs obtained with both methods in the case of the models by Koller \textit{et al}. \cite{Koller_2012} and by Batista \textit{et al}. \cite{Batista_2015}.
Small deviations are observed in the case of the Liu \textit{et al}. \cite{Liu_2014} model, but the reproducibility of RDFs by the simplified method is still very good.
%Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
The model of Weber and Kirchner \cite{Weber_2016}, on the other hand, presents RDFs for the pairs C5\textsubscript{cation}-N\textsubscript{anion} (that is, C5\textsubscript{cation} with any nitrogen atom in the anion) and C2\textsubscript{cation}-B\textsubscript{anion} with important discrepancies when rigid bodies are used.
Note that both RDFs are supposed to be affected by the orientations of the ethyl group in the cation.

\begin{table*}
	\centering
	\caption{Comparison of predicted and experimental densities for different models of \ce{[emim][B(CN)_4]} via NpT-MD simulations at $T = 298.0~\text{K}$ and $p = 0.1~\text{MPa}$. The experimental density is $1.036~\mathrm{g/cm^3}$ \cite{Doma_ska_2011}.}
	\begin{tabular}{ccccc}
		\hline
		\hline
		\ce{[emim][B(CN)_4]} model                        & 
		\multicolumn{2}{c}{Flexible ions \& PPPM-Ewald} &
		\multicolumn{2}{c}{Rigid ions \& DSF}      \\
		&
		$\rho_\text{sim}$ (g/cm\textsuperscript{3}) &
		error (\%)                                  &
		$\rho_\text{sim}$ (g/cm\textsuperscript{3}) &
		error (\%)                                  \\
		\hline
		Koller \textit{et al}. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
		Batista \textit{et al}. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
		Liu \textit{et al}. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
		Weber and Kirchner \cite{Weber_2016}         & 1.015 & 2.1 & 1.022 & 1.4  \\
		\hline
		\hline
		\label{table:props_dsf}
	\end{tabular}
\end{table*}

@@

A study of conformations was also carried out for \ce{[emim][Tf_2N]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
A CDF obtained for the dihedral angles of sequences C1-N2-C5-C6 and C2-N2-C5-C6 in \ce{[emim]^+}, which is made available in the Supplementary Material, resembles the one in Fig.~\ref{fig:dihedrals_emim}(d).
The resemblance was expected because the intramolecular parameters employed for \ce{[emim]^+} are identical in these two cases, since the corresponding models are both based on the force field developed by Canongia-Lopes and P\'{a}dua \cite{Canongia_Lopes_2006}.
However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][Tf_2N]}.
This highlights the fact that altering atomic charges can induce conformational changes and should, therefore, be accompanied by a revision of torsion parameters in some cases.
With regard to the anion \ce{[Tf_2N]^-}, Deetlefs \textit{et al}. \cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[Tf_2N]^-} is mostly found in its \textit{trans} conformation.
In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[Tf_2N]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}. \cite{Deetlefs_2006}.
This CDF also makes clear that \ce{[Tf_2N]^-} exhibits a considerable degree of flexibility.
Due to this observed behaviors of both ions, all simulations of \ce{[emim][Tf_2N]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
The relative error of this result with respect to the experimental value obtained by Tokuda \textit{et al}. \cite{Tokuda_2005} is only 1.12\%.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{Ludwig_anion}
\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[Tf_2N]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][Tf_2N]} at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.}
\label{fig:die_ntf2}
\end{figure}

@@

In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][Tf_2N]} under periodic boundary conditions.
The simulations were carried out at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
Table~\ref{table:henry} contains simulated molar densities, partial and total solvation free energies, as well as Henry's law constants ($K_s$) computed via Eq.~\eqref{eq:henry_eq}. These should be compared to the experimental data reported by Mahurin \textit{et al}. \cite{Mahurin_2010} ($K_s = 3.941 \pm 0.003 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}. \cite{Finotello_2008} ($K_s = 3.95 \pm 0.01 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][Tf_2N]}).
Uncertainties in $K_s$ were calculated using a standard error propagation formula, given by
\begin{equation}
\delta K_s = \beta K_s \sqrt{\left[ \delta^2 (\Delta G_{\text{vdW}}) + \delta^2(\Delta G_{\text{Coul}}) \right]},
\end{equation}
with uncertainties in free energy calculate using MBAR \cite{Shirts_2008}.

\begin{table*}
	\centering
	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]} at $T = 298.15~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$. The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][Tf_2N]} are, respectively, $3.941 \pm 0.003 ~\mathrm{MPa}$ \cite{Mahurin_2010} and $3.95 \pm 0.01 ~\mathrm{MPa}$ \cite{Finotello_2008}.}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{ccccccc}  
			\hline\hline
			Model & $\tilde{\rho}_\text{sim}$ & $\Delta G_\text{vdW}$  & $\Delta G_\text{Coul}$  & $\Delta G_\text{sim}$ & $K_s$ & error \\
			& (mol/dm\textsuperscript{3}) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (MPa)  & (\%) \\
			\hline
%			\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}: $K_{s}^{\text{exp}} = 38.9 \pm 0.03 ~\mathrm{atm}$ \cite{Mahurin_2010}} \\
			\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}} \\
			Koller \textit{et al}. \cite{Koller_2012} & $4.5925$ & $0.45 \pm 0.01$ & $-1.06 \pm 0.02$ & $-0.61 \pm 0.02$ & $ 4.1 \pm 0.1$ & $2.8$ \\
			Batista \textit{et al}. \cite{Batista_2015} & $4.3700$ & $0.378 \pm 0.008$ & $-1.24 \pm 0.01$  & $-0.86 \pm 0.01$ & $2.52 \pm 0.05$ & $38.9$ \\
			Liu \textit{et al}. \cite{Liu_2014} & $4.3815$ & $0.226 \pm 0.009$ & $-1.11 \pm 0.01$ & $-0.88 \pm 0.01$ & $2.46 \pm 0.05$ & $37.6$  \\
			Weber and Kirchner \cite{Weber_2016} & $4.5221$ & $0.478 \pm 0.009$ & $-1.23 \pm 0.02$ & $-0.75 \pm 0.02$ & $3.1 \pm 0.1$ & $20.3$  \\
			\hline
%			\multicolumn{7}{c}{\ce{[emim][Tf_2N]}: $K_{s}^{\text{exp}} = 39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008} }\\
			\multicolumn{7}{c}{\ce{[emim][Tf_2N]}} \\
			K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $3.99\pm 0.05$  & $0.97$  \\
			\hline\hline
			\label{table:henry} 
		\end{tabular}
	\end{adjustbox}
\end{table*}
